Auditory Scene Similarity Retrieval and Classification with Wavelet Scattering

### 2016-12-01 paper/structureScene.tex
new title
Auditory Scene Similarity Retrieval and Classification With Wavelet
Scattering
bis

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
%\title{An evaluation framework for event detection using a morphological model of acoustic scenes}
\title{Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering}

@@

\subsection{Wavelet scalogram}
Our convention for the Fourier transform of a continuous-time signal $\boldsymbol{x}(t)$ is $\boldsymbol{\hat{x}}(\omega) = \int x(t) \exp(\mathrm{i} 2\pi t \omega) \; \mathrm{d}\omega$. Note that the frequency variable $\omega$ is expressed in Hertz, not in radians per second.

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
%\title{An evaluation framework for event detection using a morphological model of acoustic scenes}
\title{Auditory Scene Similarity Retrieval and Classification with Wavelet Scattering}

@@

\subsection{Wavelet scalogram}
Our convention for the Fourier transform of a continuous-time signal $\boldsymbol{x}(t)$ is $\boldsymbol{\hat{x}}(\omega) = \int x(t) \exp(- \mathrm{i} 2\pi \omega t) \; \mathrm{d}t$. Note that the frequency variable $\omega$ is expressed in Hertz, not in radians per second.
